Personality and political beliefs across the lifespan

### 2019-12-10 scripts/manuscript.Rmd
edits to method results

keywords          : "keywords"
wordcount         : "X"
bibliography      : ["r-references.bib"]
floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
editor_options: 
  chunk_output_type: console
---

@@

#Aggregating the social and economic conservationism scale (SECs) using scoreItems from the psych package and mutate from dplyr
items <- c("Q3_1", "Q3_2","Q3_3","Q3_4","Q3_5","Q3_6","Q3_7","Q3_8","Q3_9","Q3_10","Q3_11","Q3_12" )

@@

```{r select}
#selecting the variables that we want to use, cleaning, and characterizing dataset
data <- data %>% 
  select(ResponseId, Q7, Q8, Q9, Q10, Q11,
         SEC_economic_conservatism, SEC_social_conservatism,
         Agreeableness, Conscientiousness, Openness_to_experiences, Extraversion, Emotional_stability) %>% 
  rename(Gender = Q7, 
         Age = Q8, 
         Ethnicity = Q9, 
         Political_orientation = Q10,
         Political_affiliation = Q11,
         id = ResponseId) %>% 
  janitor::clean_names() %>% 
  characterize() %>% 
  mutate(age = as.numeric(age))
```

@@

```{r table1, echo = FALSE, results = "asis"}
tidy_table_sc <- tidy %>% 
  filter(conservatism_type == 'Social conservatism') %>% 
  mutate(conservatism_score = case_when(       
      conservatism_score <= 19 & conservatism_score >= 0 ~ "[0-19]",
      conservatism_score <= 39 & conservatism_score >= 20 ~ "[20-39]",
      conservatism_score <= 59 & conservatism_score >= 40 ~ "[40-59]",
      conservatism_score <= 79 & conservatism_score >= 60 ~ "[60-79]",
      TRUE ~ "[80-100]"))
tidy_table_sc <- tidy_table_sc %>% 
  group_by(personality_trait, conservatism_score) %>% 
  summarize(mean_personality_score = mean(personality_score)) %>% 
  pivot_wider(names_from = conservatism_score, values_from = mean_personality_score)

@@

## Participants

@@

@@

@@

In order to understand the relation between conservatism and personality, we first looked at Big Five personality trait (Openness to Experience, Conscientiousness, Extraversion, Agreeableness, and Emotional Stability) scores across the spectrum of Social Conservatism (Table 1) and Economic Conservatism (Table 2) scores.

To see whether there were significant relations between Social Conservatism and the Big Five, we then ran a multiple regression predicting Social Conservatism from the Big Five personality traits. A significant regression equation was found (*F*(5, 125) = 5.051, *p* < .001), with an adjusted $R^2$ of 0.135 (Table 2). Thus, personality traits taken together explained 13.48% of variance in Social Conservatism scores. Participants' predicted Social Conservatism scores were equal to 25.82 - 3.73(Openness to Experience) + 0.07(Conscientiousness) + 1.56(Extraversion) + 3.93(Agreeableness) + 4.30(Emotional Stability). Agreeableness and Emotional Stability were significant predictors of Social Conservatism.

To see whether there were significant relations between Economic Conservatism and the Big Five, we then ran a multiple regression predicting Economic Conservatism from the Big Five personality traits. No significant regression equation was found (*F*(5, 125) = 2.207, *p* = .058) (Table 3). Thus, personality traits taken together did not significantly explain variance in Economic Conservatism scores. However, Openness to Experience was a significant predictor of Economic Conservatism.

To better understand the relation between social and economic conservatism, we examined the correlation between social and economic conservatism scores, and found it to be r = 0.65. Neither social nor economic extraversion were strongly correlated with any of the Big Five personality traits.

@@

untidy_cor <- untidy %>% 
  select(-c(1:6)) %>% 
  rename('Social conservatism' = 'social_conservatism',
         'Economic conservatism' = 'economic_conservatism',
         'Openness to experiences' = 'openness_to_experiences',
         'Emotional stability' = 'emotional_stability')
cor_conservatism_ocean <- round(cor(untidy_cor),2)
upper_s<-cor_conservatism_ocean
upper_s[upper.tri(cor_conservatism_ocean)]<-""
upper_s<-as.data.frame(upper_s) %>%
  apa_table(
    caption = "Correlation Matrix for Conservatism and Big Five Personality Traits",
  landscape = TRUE,
  font_size = "tiny")

heatmap(cor_conservatism_ocean,
        Rowv = NA,
        Colv = NA,
        main = "Correlation Heatmap",
        margins = c(15,15),
        col = viridis(100, direction = -1))
```

```{r figure1, fig.cap= ""}
ggplot(tidy, aes(x = personality_score, y = conservatism_score, color = personality_trait)) +
  geom_smooth(se=FALSE, method = "lm")+
  labs(title = "Conservatism by Personality Traits", subtitle = "Big 5 traits self-reported by adults aged 20-68",
       x= "How strongly participants identify with the personality trait", y = "Conservatism", 
       color = "Personality Trait")+
  theme_minimal()+
  scale_color_viridis_d() +
  facet_wrap(~conservatism_type)
```

>>>>

keywords          : "keywords"
wordcount         : "X"
bibliography      : ["r-references.bib"]
floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
editor_options: 
  chunk_output_type: console
---

@@

#Aggregating the social and economic conservationism scale (SECs) using scoreItems from the psych package and mutate from dplyr
items <- c("Q3_1", "Q3_2","Q3_3","Q3_4","Q3_5","Q3_6","Q3_7","Q3_8","Q3_9","Q3_10","Q3_11","Q3_12")

@@

```{r select}
#selecting the variables that we want to use, cleaning, and characterizing dataset
data <- data %>% 
  select(ResponseId, Q7, Q8, Q9, Q10, Q11, Duration__in_seconds_,
         SEC_economic_conservatism, SEC_social_conservatism,
         Agreeableness, Conscientiousness, Openness_to_experiences, Extraversion, Emotional_stability) %>% 
  rename(Gender = Q7, 
         Age = Q8, 
         Ethnicity = Q9, 
         Political_orientation = Q10,
         Political_affiliation = Q11,
         id = ResponseId) %>% 
  janitor::clean_names() %>% 
  characterize() %>% 
  mutate(age = as.numeric(age))
```

@@

```{r table1, echo = FALSE, results = "asis"}
#this table is of the mean personality trait scores by social conservatism scores
tidy_table_sc <- tidy %>% 
  filter(conservatism_type == 'Social conservatism') %>%
  mutate(conservatism_score = case_when(       
      conservatism_score <= 19 & conservatism_score >= 0 ~ "[0-19]",
      conservatism_score <= 39 & conservatism_score >= 20 ~ "[20-39]",
      conservatism_score <= 59 & conservatism_score >= 40 ~ "[40-59]",
      conservatism_score <= 79 & conservatism_score >= 60 ~ "[60-79]",
      TRUE ~ "[80-100]"))
tidy_table_sc <- tidy_table_sc %>%
  group_by(personality_trait, conservatism_score) %>% 
  summarize(mean_personality_score = mean(personality_score)) %>% 
  pivot_wider(names_from = conservatism_score, values_from = mean_personality_score)

@@

```{r, include = FALSE}
#Age statistics
mean_age <- mean(as.numeric(data$age)) %>% round(2)
sd_age <- sd(as.numeric(data$age)) %>% round(2)
r1_age <- range(as.numeric(data$age))[1]
r2_age <- range(as.numeric(data$age))[2]

#Number of participants
n <- nrow(data)

#Ethnicity
#I'm creating a function that will spit out the percentage of people with a given ethnicity, including a % sign
percent_ethn <- function(pos){
  paste(((table(data$ethnicity)[[pos]]/n) *100) %>% round(1), "%", sep = "")}
black <-percent_ethn(1)
asian <- percent_ethn(2)
white <- percent_ethn(3)
hispanic <- percent_ethn(4)
native <- percent_ethn(5)
other <- percent_ethn(6)

#Gender
percent_gen <- function(pos){
  paste(((table(data$gender)[[pos]]/n) *100) %>% round(1), "%", sep = "")}
female <- percent_gen(1)
male <- percent_gen(2)

#politicial affiliation
percent_pa <- function(pos){
  paste(((table(data$political_affiliation)[[pos]]/n) *100) %>% round(1), "%", sep = "")}
democrat <- percent_pa(1)
republican <- percent_pa(6)
no_party <- percent_pa(4)
other_n <- table(data$political_affiliation)[[2]]+
  table(data$political_affiliation)[[3]]+
  table(data$political_affiliation)[[5]]
other <- paste(((other_n/n) *100) %>% round(1), "%", sep = "")

#Duration
data <- data %>% 
  mutate(duration_in_seconds = as.numeric(duration_in_seconds))
duration_m <- mean(data$duration_in_seconds)/60
duration_sd <- sd(data$duration_in_seconds)/60
```
## Participants

Two-hundred U.S. adults were recruited via Amazon Mechanical Turk to participate in a study listed as "Psychology and society survey." Participants were removed for completing the survey quicker than predetermined time cutoffs or failing to pass attention checks. Of the remaining `r n` participants, who were `r r1_age` to `r r2_age` years old (*M* = `r mean_age`, *SD* = `r sd_age`), `r female` identified as female and `r male` identified as male, while `r white` identified as White of Caucasian, `r black` as African American or Black, `r hispanic` as Hispanic or Latinx, `r asian` as Asian or Asian American, `r native` as Native American, and `r other` as "Other." The sample leaned liberal, with `r democrat` affiliated with the Democratic Party, `r republican` affiliated with the Republican Party, `r no_party` affiliated with no party, and `r other` affiliated with the Green Party, Libertarian Party, or another party. The participants were compensated $1.50 for completing the survey, which took on average `r duration_m` minutes (*SD* = `r duration_sd`).

@@

**Personality.** To assess personality traits (openness to experiences, conscientiousness, extraversion, agreeableness, and emotional stability), respondents completed the Ten Item Personality Inventory [@gosling2003very]. Participants were asked to indicate the extent to which they agreed or disagreed with statements describing themselves (e.g. “Extraverted, enthusiastic”; “Critical, quarrelsome”). Respondents rated each statement on a 7-point likert scale (1 = Strongly Disagree to 7 = Strongly Agree). Responses were coded such that higher values reflected greater identification with the personality trait.

**Social and Economic Conservatism.** To assess participant levels of conservatism, respondents completed the 12-item Social and Economic Conservatism Scale [@everett201312]. Participants were asked to indicate the extent to which they feel positively or negatively about seven social issues and five economic issues (eg. Abortion; Fiscal Responsibility). Respondents rated each issue on a 100-point scale (0 indicates greater negativity and 100 indicates greater positivity). Responses were coded such that higher values reflected greater levels of conservatism.

**Additional Measures.** Incidental affect was induced via video clips [@schaefer2010]. Clips from _The Shining_ and _The Blair Witch Project_ were used to induce fear, clips from _Seven_ and _Schindler’s List_ were used to induce anger, and clips from _Blue_ were used to induce no emotion. Participants also read a speech on the prevalence of homelessness in the United States and a corresponding policy varying in complexity and affiliation.

Participants completed additional measures, including an adjusted PANAS Affect Scale assessing current emotional state [@watson1988development], the 18-Point Need for Cognition Scale assessing need for cognition [@cacioppo1984efficient], the 10-Point Emotion Regulation Questionnaire assessing the use of two emotional regulation strategies, cognitive reappraisal and expressive supression [@gross2003individual], and demographic information, including gender, ethnicity, age, and political orientation and affiliation.

@@

Participants accessed the survey through the Amazon Mechanical Turk website. Once informed consent was confirmed, participants were randomly assigned to watch a video intended to induce primarily fear, anger, or no emotion. After watching the video, each participant was presented with information describing the prevalance of homelessness in the United States. Participants were then randomly assigned to read a policy statement addressing homelessness that was either simple or complex, and liberal or conservative, and were then asked to answer questions measuring their beliefs about the policy. Additional measures followed measuring social and economic conservatism, personality traits, current affective state, neeed for cognition, and emotional regulation. Participants concluded the study by providing demographic information.

@@

In order to explore relation between conservatism and personality, we created a table of the Big Five personality trait (openness to experiences, conscientiousness, extraversion, agreeableness, and emotional stability) scores across different levels of social (see Table 1) and economic (see Table 2) conservatism.

To see whether there were significant relations between social conservatism and the Big Five traits, we then ran a multiple regression predicting social conservatism from the Big Five personality traits. We found that together the personality traits explain about 13.5% of the variance in social conservatism scores, *F*(5, 125) = 5.05, *p* < .001, with an adjusted $R^2$ of .14 (see Table 3). We found that agreeablessness, $\beta$ = 3.93, *t*(125) = 2.40, *p* = .018, and emotional stability, $\beta$ = 4.30, *t*(125) = 2.37, *p* = .020, significantly predict social conservatism, such that, controlling for the other personality traits, those who scored higher on agreeableness and emotional stability measures tended to also score higher on the social conservatism measure. Additionally, openness to experiences margionally predicted social conservatism, $\beta$ = -3.73, *t*(125) = -1.96, *p* = .052, such that, controlling for other personality traits, those who scored higher on conservatism tended to score lower on the openness to experience measure.

To see whether there were significant relations between economic conservatism and the Big Five traits, we then ran a multiple regression predicting economic conservatism from the Big Five personality traits. The personality traits taken together did not significantly explain variance in economic conservatism scores, *F*(5, 125) = 2.21, *p* = .058 (see Table 4). However, openness to experience was a significant predictor of economic conservatism, $\beta$ = -3.79, *t*(125) = -2.35, *p* = .021, such that, controlling for other personality traits, those who scored high on economic conservatism subscale tended to score lower on the openness to experiences measure.

To better understand the relation between social and economic conservatism, we examined the correlation between social and economic conservatism scores, and found it to be *r* = .65. Neither social nor economic extraversion were strongly correlated with any of the Big Five personality traits (see Figure 1).

@@

untidy_cor <- untidy %>% 
  select(-c(1:7)) %>% 
  rename('Social conservatism' = 'social_conservatism',
         'Economic conservatism' = 'economic_conservatism',
         'Openness to experiences' = 'openness_to_experiences',
         'Emotional stability' = 'emotional_stability')
cor_conservatism_ocean <- round(cor(untidy_cor),2)
upper_s<-cor_conservatism_ocean
upper_s[upper.tri(cor_conservatism_ocean)]<-""
upper_s<-as.data.frame(upper_s) %>%
  apa_table(
    caption = "Correlation Matrix for Conservatism and Big Five Personality Traits",
  landscape = TRUE,
  font_size = "tiny")

```{r figure1, fig.cap="A correlation heatmap demonstrating the correlations between the Big Five personality traits and social and economic conservatism."}
heatmap(cor_conservatism_ocean,
        Rowv = NA,
        Colv = NA,
        main = "Correlation Heatmap",
        margins = c(15,15),
        col = viridis(100, direction = -1))
```

```{r figure2, fig.cap= "We found a significant positive relation between emotional stability and social conservatism, a positive relation between agreeableness and social conservatism, and a negative relation between openness to experiences and economic conservatism.", fig.height = 10, fig.width = 8}
ggplot(tidy, aes(x = personality_score, y = conservatism_score, color = conservatism_type)) +
  geom_smooth(se=FALSE, method = "lm")+
  labs(title = "Conservatism by Personality Traits", subtitle = "Big 5 traits self-reported by adults aged 20-68",
       x= "How strongly participants identify with the personality trait", y = "Conservatism score", 
       color = "Conservatism type")+
  theme_minimal()+
  scale_color_viridis_d() +
  facet_wrap(~personality_trait, ncol = 1)
```

### 2019-12-10 scripts/manuscript.tex
edits to method results

\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

\linenumbers

@@

@@

@@

In order to understand the relation between conservatism and
personality, we first looked at Big Five personality trait (Openness to
Experience, Conscientiousness, Extraversion, Agreeableness, and
Emotional Stability) scores across the spectrum of Social Conservatism
(Table 1) and Economic Conservatism (Table 2) scores.

To see whether there were significant relations between Social
Conservatism and the Big Five, we then ran a multiple regression
predicting Social Conservatism from the Big Five personality traits. A
significant regression equation was found (\emph{F}(5, 125) = 5.051,
\emph{p} \textless{} .001), with an adjusted \(R^2\) of 0.135 (Table 2).
Thus, personality traits taken together explained 13.48\% of variance in
Social Conservatism scores. Participants' predicted Social Conservatism
scores were equal to 25.82 - 3.73(Openness to Experience) +
0.07(Conscientiousness) + 1.56(Extraversion) + 3.93(Agreeableness) +
4.30(Emotional Stability). Agreeableness and Emotional Stability were
significant predictors of Social Conservatism.

To see whether there were significant relations between Economic
Conservatism and the Big Five, we then ran a multiple regression
predicting Economic Conservatism from the Big Five personality traits.
No significant regression equation was found (\emph{F}(5, 125) = 2.207,
\emph{p} = .058) (Table 3). Thus, personality traits taken together did
not significantly explain variance in Economic Conservatism scores.
However, Openness to Experience was a significant predictor of Economic
Conservatism.

To better understand the relation between social and economic
conservatism, we examined the correlation between social and economic
conservatism scores, and found it to be r = 0.65. Neither social nor
economic extraversion were strongly correlated with any of the Big Five
personality traits.

@@

@@

@@

@@

@@

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/correlations-1.pdf}
\caption{}
\end{figure}

\includegraphics{manuscript_files/figure-latex/figure1-1.pdf}

>>>>

\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother

@@

Two-hundred U.S. adults were recruited via Amazon Mechanical Turk to
participate in a study listed as \enquote{Psychology and society
survey.} Participants were removed for completing the survey quicker
than predetermined time cutoffs or failing to pass attention checks. Of
the remaining 131 participants, who were 20 to 68 years old (\emph{M} =
40.55, \emph{SD} = 11.98), 54.2\% identified as female and 45.8\%
identified as male, while 77.1\% identified as White of Caucasian, 7.6\%
as African American or Black, 6.1\% as Hispanic or Latinx, 5.3\% as
Asian or Asian American, 0.8\% as Native American, and 9.2\% as
\enquote{Other.} The sample leaned liberal, with 45\% affiliated with
the Democratic Party, 23.7\% affiliated with the Republican Party,
22.1\% affiliated with no party, and 9.2\% affiliated with the Green
Party, Libertarian Party, or another party. The participants were
compensated \$1.50 for completing the survey, which took on average
10.43 minutes (\emph{SD} = 3.34).

@@

\textbf{Personality.} To assess personality traits (openness to
experiences, conscientiousness, extraversion, agreeableness, and
emotional stability), respondents completed the Ten Item Personality
Inventory (Gosling, Rentfrow, \& Swann Jr, 2003). Participants were
asked to indicate the extent to which they agreed or disagreed with
statements describing themselves (e.g. \enquote{Extraverted,
enthusiastic}; \enquote{Critical, quarrelsome}). Respondents rated each
statement on a 7-point likert scale (1 = Strongly Disagree to 7 =
Strongly Agree). Responses were coded such that higher values reflected
greater identification with the personality trait.

\textbf{Social and Economic Conservatism.} To assess participant levels
of conservatism, respondents completed the 12-item Social and Economic
Conservatism Scale (Everett, 2013). Participants were asked to indicate
the extent to which they feel positively or negatively about seven
social issues and five economic issues (eg. Abortion; Fiscal
Responsibility). Respondents rated each issue on a 100-point scale (0
indicates greater negativity and 100 indicates greater positivity).
Responses were coded such that higher values reflected greater levels of
conservatism.

\textbf{Additional Measures.} Incidental affect was induced via video
clips (Schaefer, Nils, Sanchez, \& Philippot, 2010). Clips from
\emph{The Shining} and \emph{The Blair Witch Project} were used to
induce fear, clips from \emph{Seven} and \emph{Schindler's List} were
used to induce anger, and clips from \emph{Blue} were used to induce no
emotion. Participants also read a speech on the prevalence of
homelessness in the United States and a corresponding policy varying in
complexity and affiliation.

Participants completed additional measures, including an adjusted PANAS
Affect Scale assessing current emotional state (Watson, Clark, \&
Tellegen, 1988), the 18-Point Need for Cognition Scale assessing need
for cognition (Cacioppo, Petty, \& Feng Kao, 1984), the 10-Point Emotion
Regulation Questionnaire assessing the use of two emotional regulation
strategies, cognitive reappraisal and expressive supression (Gross \&
John, 2003), and demographic information, including gender, ethnicity,
age, and political orientation and affiliation.

@@

In order to explore relation between conservatism and personality, we
created a table of the Big Five personality trait (openness to
experiences, conscientiousness, extraversion, agreeableness, and
emotional stability) scores across different levels of social (see Table
1) and economic (see Table 2) conservatism.

To see whether there were significant relations between social
conservatism and the Big Five traits, we then ran a multiple regression
predicting social conservatism from the Big Five personality traits. We
found that together the personality traits explain about 13.5\% of the
variance in social conservatism scores, \emph{F}(5, 125) = 5.05,
\emph{p} \textless{} .001, with an adjusted \(R^2\) of .14 (see Table
3). We found that agreeablessness, \(\beta\) = 3.93, \emph{t}(125) =
2.40, \emph{p} = .018, and emotional stability, \(\beta\) = 4.30,
\emph{t}(125) = 2.37, \emph{p} = .020, significantly predict social
conservatism, such that, controlling for the other personality traits,
those who scored higher on agreeableness and emotional stability
measures tended to also score higher on the social conservatism measure.
Additionally, openness to experiences margionally predicted social
conservatism, \(\beta\) = -3.73, \emph{t}(125) = -1.96, \emph{p} = .052,
such that, controlling for other personality traits, those who scored
higher on conservatism tended to score lower on the openness to
experience measure.

To see whether there were significant relations between economic
conservatism and the Big Five traits, we then ran a multiple regression
predicting economic conservatism from the Big Five personality traits.
The personality traits taken together did not significantly explain
variance in economic conservatism scores, \emph{F}(5, 125) = 2.21,
\emph{p} = .058 (see Table 4). However, openness to experience was a
significant predictor of economic conservatism, \(\beta\) = -3.79,
\emph{t}(125) = -2.35, \emph{p} = .021, such that, controlling for other
personality traits, those who scored high on economic conservatism
subscale tended to score lower on the openness to experiences measure.

To better understand the relation between social and economic
conservatism, we examined the correlation between social and economic
conservatism scores, and found it to be \emph{r} = .65. Neither social
nor economic extraversion were strongly correlated with any of the Big
Five personality traits (see Figure 1).

@@

\hypertarget{ref-cacioppo1984efficient}{}
Cacioppo, J. T., Petty, R. E., \& Feng Kao, C. (1984). The efficient
assessment of need for cognition. \emph{Journal of Personality
Assessment}, \emph{48}(3), 306--307.

@@

\hypertarget{ref-everett201312}{}
Everett, J. A. (2013). The 12 item social and economic conservatism
scale (secs). \emph{PloS One}, \emph{8}(12), e82131.

@@

\hypertarget{ref-gosling2003very}{}
Gosling, S. D., Rentfrow, P. J., \& Swann Jr, W. B. (2003). A very brief
measure of the big-five personality domains. \emph{Journal of Research
in Personality}, \emph{37}(6), 504--528.

\hypertarget{ref-gross2003individual}{}
Gross, J. J., \& John, O. P. (2003). Individual differences in two
emotion regulation processes: Implications for affect, relationships,
and well-being. \emph{Journal of Personality and Social Psychology},
\emph{85}(2), 348.

@@

\hypertarget{ref-schaefer2010}{}
Schaefer, A., Nils, F., Sanchez, X., \& Philippot, P. (2010). Assessing
the effectiveness of a large database of emotion-eliciting films: A new
tool for emotion researchers. \emph{Cognition and Emotion},
\emph{24}(7), 1153--1172.

\hypertarget{ref-watson1988development}{}
Watson, D., Clark, L. A., \& Tellegen, A. (1988). Development and
validation of brief measures of positive and negative affect: The panas
scales. \emph{Journal of Personality and Social Psychology},
\emph{54}(6), 1063.

@@

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/figure1-1.pdf}
\caption{\label{fig:figure1}A correlation heatmap demonstrating the
correlations between the Big Five personality traits and social and
economic conservatism.}
\end{figure}

\begin{figure}
\centering
\includegraphics{manuscript_files/figure-latex/figure2-1.pdf}
\caption{\label{fig:figure2}We found a significant positive relation between
emotional stability and social conservatism, a positive relation between
agreeableness and social conservatism, and a negative relation between
openness to experiences and economic conservatism.}
\end{figure}
